Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-09 main.tex
sequents

\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

@@

\newcommand{\set}[1]{\{#1\}}

@@

\begin{document}
\bstctlcite{refs:BSTcontrol}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}

@@

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage{dashbox}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}

\usepackage{cmll}

\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

\newcommand{\axr}{\mathsf{ax}}
\newcommand{\cutr}{\mathsf{cut}}
\newcommand{\mixr}{\mathsf{mix}}
\newcommand{\conr}{\mathsf{ctr}}
\newcommand{\weakr}{\mathsf{wk}}

@@

\newcommand{\set}[1]{\{#1\}}
\newcommand{\sqn}[1]{\vdash#1}

\newcommand{\sublist}[1]{\set{#1}}
\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}

\newcommand{\form}[1]{\mathrm{fm}(#1)}

@@

\begin{document}
\vlnosmallleftlabels

\bstctlcite{refs:BSTcontrol}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}

@@

A \bfit{substitution} is a function $\sigma\colon\VAR\to\TERM$ that is
the identity almost everywhere. We denote substitutions as
$\sigma=\sublist{\subst{x_1}{t_1},\ldots,\subst{x_n}{t_n}}$, where
$\sigma(x_i)=t_i$ for $i=1..n$ and $\sigma(x)=x$ for all
$x\notin\set{x_1,\ldots,x_n}$. 
We write $A\sigma$ for the formula
obtained from $A$ by applying $\sigma$, i.e., by simultaneously
replacing all occurrences of $x_i$ by $t_i$.
A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variables.

@@

\begin{figure}[!t]
  \begin{center}
    \framebox{%
      $
      \begin{array}{@{}c@{}}
        \dbox{%
          $
          \begin{array}{c}
            \vlinf{\axr}{}{\sqn{a,\cneg a}}{}
            \qquad
            \vlinf{\ttt}{}{\sqn{\ttt}}{}
            \qquad
            \vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}
            \\ \\[-1ex]
            \vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}
            \qquad
            \vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}
            \\ \\[-1ex]
            \vlinf{\exists}{}{\sqn{\Gamma,\exists x.A}}{\sqn{\Gamma,A\ssubst{x}{t}}}
            \qquad
            \vlinf{\forall}{\text{($x$ not free in $\Gamma$)}}{\sqn{\Gamma,\forall x.A}}{\sqn{\Gamma,A}}
          \end{array}
          $%
        }%
        \\\\[-1ex]
        \vlinf{\conr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma,A,A}}
        \qquad
        \vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}
      \end{array}
      $
    }
  \end{center}
  \caption{Sequent calculi $\FOLK$ (all rules) and $\FOMLL$ (rules in the dashed box)}
  \label{fig:LK1}
\end{figure}

\bfit{Sequents}, denoted by $\Gamma,\Delta,\ldots$, are finite
multisets of formulas, written as lists, separated by comma. The
\bfit{corresponding formula} of a sequent $\Gamma=A_1,A_2,\ldots,A_n$
is the disjunction of its formulas: $\form\Gamma=A_1\vlor
A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
corresponding formula is.
